Literature Review - Informal

### 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
added comments

Game theoretic models are generally the go-to method for understanding multi-agent systems. As such
they fit into all of the categories in this chapter (except, perhaps, swarms) since Dec-POMDP and
MARL methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset
of Partially Observed Stochastic Games (POSG), in which all agents use the same payoff. Game theory
can, therefore, be used in an applied capacity to direct task allocation across heterogenous teams.

@@

@@

Reinforcement learning extends the Markov Decision Process problem by considering the case where the
payoff model is not known. This, of course, is the case for most real world environments. As such,
MARL algorithms can perhaps be considered to be more applicable than Dec-POMDP models. Fortunately,
MARL has picked up a lot of traction in research recently, with a large body dedicated towards
solving the many problems it presents.

@@

@@

>>>>

Game theoretic models are generally the go-to method for understanding
multi-agent systems. As such they fit into all of the categories in
this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
methods have both used game theory to support their frameworks. In
fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
(POSG), in which all agents use the same payoff. \fr{That's an
  interesting remark. It might be worth to check whether we can
  leverage on this and similar observations.} Game theory can,
therefore, be used in an applied capacity to direct task allocation
across heterogenous teams.

@@

\fr{The game-theoretic approaches described above might suffer from the
  same drawbacks identified above for fault detection, namely reliance
  on communication and on a single central authority. I'd rather
  favour distributed approaches. Also, market-based mechanisms and
  negotiation might lead us to a completely different direction.}

@@

Reinforcement learning extends the Markov Decision Process problem by
considering the case where the payoff model is not known. This, of
course, is the case for most real world environments. As such, MARL
algorithms can perhaps be considered to be more applicable than
Dec-POMDP models.
\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}

Fortunately, MARL has picked up a lot of traction in
research recently, with a large body dedicated towards solving the
many problems it presents.

@@

\fr{This looks like an interesting, non-trivial problem: how can we
  represent the other agents within the agent model itself, in order
  to improve learning in MARL? Shall we have a closer look at this problem?}

@@

\fr{All the above looks extremely interesting. I would explore the
  above for decentralized and partially observable settings. What
  results are mentioned \cite{SchwartzMulti-agentApproach} under such
  assumptions?}
